\ \ \ \ 
\texttt{[1] Aday, James Brian. “Competitive Advantage or Market Saturation: An In-Depth Comparison of Flash-Sale Sites Through Content Analysis.” Taylor; Francis, Nov. 2014,}
\url{https://www.tandfonline.com/doi/abs/10.1080/19368623.2014.905815}.

\texttt{[2] Chen, ChenCheng-Hao. “Exploring Electronic Word-of-Mouth (EWOM) in The Consumer Purchase Decision-Making Process: The Case of Online Holidays – Evidence from United Kingdom (UK) Consumers.” Taylor; Francis,}
\url{ https://www.tandfonline.com/doi/abs/10.1080/10548408.2014.956165.}

\texttt{[3] Chi, Hsin  Kuang. “The Impact of Brand Awareness on Consumer Purchase Intention: The Mediating Effect of Perceived Quality and Brand Loyalty.” The Impact of Brand Awareness on Consumer Purchase Intention: The Mediating Effect of Perceived Quality and Brand Loyalty, Feb. 2009,} \url{http://203.72.2.146/bitstream/987654321/27159/1/The+Impact+of+Brand.pdf}.

\texttt{[4] Chinthalapati, Raju. “Dynamic Price in Retail Market.” Learning Dynamic Prices in MultiSeller Electronic Retail Markets with Price Sensitive Customers, Stochastic Demands, and Inventory Replenishments - IEEE Journals; Magazine,}
\url{https://ieeexplore.ieee.org/abstract/document/1603740}.

\texttt{[5] Day, George S. "A Two-Dimensional Concept of Brand Loyalty." SpringerLink. Springer, Berlin, Heidelberg, 01 Jan. 1976. Web. 03 Apr. 2020.}
\url{https://link.springer.com/chapter/10.1007%2F978-3-642-51565-1_26}.

\texttt{[6] Dwyer, Ehrenberg, "Consumers' Trust in a Brand and the Link to Brand Loyalty." Journal of Market-Focused Management. Kluwer Academic Publishers, 01 Jan. 1991. Web. 03 Apr. 2020.} \url{https://link.springer.com/article/10.1023/A:1009886520142}

\texttt{[7] Gartner,“Optimal Traffic Assignment with Elastic Demands: A Review Part I. Analysis Framework.” Traffic Assignment on Elastic Demands, 1 May 1980,}
\url{https://pubsonline.informs.org/doi/abs/10.1287/trsc.14.2.174}.

\texttt{[8] Jacoby, Jacob,“Brand Loyalty Vs. Repeat Purchasing Behavior - Jacob Jacoby, David B. Kyner, 1973.” SAGE Journals,} 
\url{https://journals.sagepub.com/doi/abs/10.1177/002224377301000101}.

\texttt{[9] Mittal, Banwari. “Measuring Purchase‐Decision Involvement.” Wiley Online Library, John Wiley; Sons, Ltd, 6 Sept. 2006,} 
\url{https://onlinelibrary.wiley.com/doi/abs/10.1002/mar.4220060206}.

\texttt{[10] Montreuil, Benoit. “A Modelling Framework for Integrating Layout Design and Flow Network Design.” SpringerLink, Springer, Berlin, Heidelberg, 1 Jan. 1991,}
\url{https://link.springer.com/chapter/10.1007/978-3-642-84356-3\_8}.

\texttt{[11] OpenStax. "Principles of Economics."\textit{Principles of Economics,}}
\url{https://opentextbc.ca/principlesofeconomics/}

\texttt{[12] Schwartz, Robyn. “PatentApplicationPublication.” PatentApplicationPublication, May 2013,}
\url{https://patentimages.storage.googleapis.com/4d/5a/8e/906078f1d451cf/US20130138498A1.pdf}.

\texttt{[13] Zhang, Mingyang, Juliang Zhang, T.C.E. Cheng, and Guowei Hua. "Why and How Do Branders Sell New Products on Flash Sale Platforms?" European Journal of Operational Research. North-Holland, 08 Mar. 2018. Web. 03 Apr. 2020.}
\url{https://www.sciencedirect.com/science/article/abs/pii/S0377221718302017}