\ \ \ \ Flash sale is an event where the owners of the stores aim to attract buyers by giving a huge discount on the products which couldn’t be easily found elsewhere. Obviously, people somehow want to save money by buying discounted products, and since there’s a limited amount of products, people stampede in to buy products and usually damage other products accidentally. It’ll be beneficial if we could alter the floor layout to minimize the damage caused by the buyers to the products, while keep being able to make a high potential profit or earning from the event. Hosting the flash sale with some specific layout will help increase the utility of the store, and increase the profit of the host. \newline\par
In this report, we identified how damage would be caused by the buyers by creating a model of chaos and messiness of floor layout, we showed that the popularity of a product depends on some properties of products; price (affordability), discount, demands, and brand. The messiness of the store depends on the popularity of the product that is selling in that store and the area of the store. To find the model of damage, we consider chaos instead of messiness. Chaos is defined around every path and corner. To compare two floor-layouts, we can simply compare the chaos of each model. \newline\par 
From the given layout, we analyze the chaos of the floor plan and found that the problem of this floor plan is the fact that there are too many corners, and corners contribute large value to chaos. It’s sensible that more corners cause more damage since when people are running uncontrollably, collision and damage will occur. In order to minimize the damage, we propose a new floor plan and provided proof that the proposed floor plan definitely gives small chaos and smaller potential damage from buyers’ clumsiness. \newline\par
The proposed floor plan uses the structure of the layout to force the people to walk systematically with an overall corner being reduced and with all corners having the products that can be damaged all removed. We can confirm that less collision will happen and as a result, lower potential damage dealt with the product. We consider all permutation of the department and choose the permutation giving the best result. Then for each department, we organize it the way that the store switch between the one with more messiness and the one with less messiness. This would make the damage be minimized and make this floor plan the best one we can generate. \newline